A New Model to Predict Survival in Patients with End-Stage Liver Disease

### 2022-06-19 analysis/article.Rmd
feat: cite ameld with zenodo doi

author:
    - Sebastian Gibb:
        email: mail@sebastiangibb.de
        institute: [ILM, KAINS]
        correspondence: true
    - Thorsten Kaiser:
        email: thorsten.kaiser@medizin.uni-leipzig.de
        institute: ILM
        correspondence: false
institute:
    - ILM: Institute of Laboratory Medicine, Clinical Chemistry and Molecular Diagnostics, University Hospital Leipzig, Paul-List-Str. 13-15, D-04103 Leipzig, Germany.
    - KAINS: Anesthesiology and Intensive Care Medicine, University Hospital Greifswald, Ferdinand-Sauerbruch-Straße, D-17475 Greifswald, Germany.
date: "`r Sys.Date()`"
bibliography:
  - "`r rprojroot::find_rstudio_root_file('analysis', 'bibliography', 'bibliography.bib')`"
  - "`r rprojroot::find_rstudio_root_file('analysis', 'bibliography', 'rpackages', 'article.bib')`"
output:
  bookdown::html_document2:
    pandoc_args: # pandoc_args doesn't support r evaluation
      - --lua-filter=pandoc/lua-filters/scholarly-metadata.lua
      - --lua-filter=pandoc/lua-filters/author-info-blocks.lua
  bookdown::word_document2:
    pandoc_args: # pandoc_args doesn't support r evaluation
      - --lua-filter=pandoc/lua-filters/scholarly-metadata.lua
      - --lua-filter=pandoc/lua-filters/author-info-blocks.lua
---

```{r knitr_setup, include=FALSE}
knitr::write_bib(
    c(
        "base",
        "targets", "workflowr",
        "gtsummary",
        "mlr3", "mlr3proba", "zlog",
        "survival", "glmnet", "penalized", "ranger", "randomForestSRC",
        "xgboost", "survivalsvm", "survivalmodels", "timeROC"
    ),
    file = rprojroot::find_rstudio_root_file(
        "analysis", "bibliography", "rpackages", "article.bib"
    )
)
```

@@

- comparable mortality?
- retrospective analysis
- single center
- unknown cause of death (death with vs of end-stage liver disease)
- bias caused by LTx censorship?
-->
# Data and software availability

**TODO** add zenodo links here.
The complete code and reproducible analysis could be found at
https://ampel-leipzig.github.io/ampel-leipzig-meld/.
Additionally all data are available in the `ameld` R package at
https://github.com/ampel-leipzig/ameld for further investigations.

>>>>

author:
    - Sebastian Gibb:
        email: mail@sebastiangibb.de
        institute: [ILM, KAINS]
        correspondence: true
    - Thorsten Kaiser:
        email: thorsten.kaiser@medizin.uni-leipzig.de
        institute: ILM
        correspondence: false
institute:
    - ILM: Institute of Laboratory Medicine, Clinical Chemistry and Molecular Diagnostics, University Hospital Leipzig, Paul-List-Str. 13-15, D-04103 Leipzig, Germany.
    - KAINS: Anesthesiology and Intensive Care Medicine, University Hospital Greifswald, Ferdinand-Sauerbruch-Straße, D-17475 Greifswald, Germany.
date: "`r Sys.Date()`"
bibliography:
  - "`r rprojroot::find_rstudio_root_file('analysis', 'bibliography', 'bibliography.bib')`"
  - "`r rprojroot::find_rstudio_root_file('analysis', 'bibliography', 'rpackages', 'article.bib')`"
  - "`r rprojroot::find_rstudio_root_file('analysis', 'bibliography', 'rpackages', 'ameld.bib')`"
  - "`r rprojroot::find_rstudio_root_file('analysis', 'bibliography', 'rpackages', 'zlog.bib')`"
output:
  bookdown::html_document2:
    pandoc_args: # pandoc_args doesn't support r evaluation
      - --lua-filter=pandoc/lua-filters/scholarly-metadata.lua
      - --lua-filter=pandoc/lua-filters/author-info-blocks.lua
  bookdown::word_document2:
    pandoc_args: # pandoc_args doesn't support r evaluation
      - --lua-filter=pandoc/lua-filters/scholarly-metadata.lua
      - --lua-filter=pandoc/lua-filters/author-info-blocks.lua
---

```{r knitr_setup, include=FALSE}
knitr::write_bib(
    c(
        "base",
        "targets", "workflowr",
        "gtsummary",
        "mlr3", "mlr3proba",
        "survival", "glmnet", "penalized", "ranger", "randomForestSRC",
        "xgboost", "survivalsvm", "survivalmodels", "timeROC"
    ),
    file = rprojroot::find_rstudio_root_file(
        "analysis", "bibliography", "rpackages", "article.bib"
    )
)
cat(
    gsub("@Manual\\{", "@Manual\\{R-ameld", toBibtex(citation("ameld"))),
    file = rprojroot::find_rstudio_root_file(
        "analysis", "bibliography", "rpackages", "ameld.bib"
    )
)
cat(
    gsub("@Manual\\{", "@Manual\\{R-zlog", toBibtex(citation("zlog"))),
    file = rprojroot::find_rstudio_root_file(
        "analysis", "bibliography", "rpackages", "zlog.bib"
    )
)
```

@@

- comparable mortality?
- retrospective analysis
- single center
- unknown cause of death (death with vs of end-stage liver disease)
- bias caused by LTx censorship?
-->

# Data and software availability

The complete code and reproducible analysis could be found at
https://ampel-leipzig.github.io/ampel-leipzig-meld/.
Additionally all data are available in the `ameld` R package [@R-ameld] at
https://github.com/ampel-leipzig/ameld
[![DOI](https://zenodo.org/badge/DOI/10.5281/zenodo.6666018.svg)](https://doi.org/10.5281/zenodo.6666018)
for further investigations.
